---
title: "Homework 2"
author: "Luo Bingjun 2017013573"
date: '2019-04-05'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 4.19
### (a)
$$(X_1-\mu)'\Sigma^{-1}(X_1-\mu)\sim \chi_6^2$$

### (b)
Denote $c_i=\frac{1}{n},\ i=1,2,\cdots,n$

Then
$$\bar{X}=\sum_{i=1}^nc_iX_i\sim N_6(\mu,\frac{1}{n}\Sigma)$$
$$\sqrt{n}(\bar{X}-\mu)\sim N_6(0,\Sigma)$$

### (c)
$$(n-1)S=\sum_{i=1}^n(X_i-\bar{X})(X_i-\bar{X})'\sim W_6(\Sigma, n-1)$$

## 4.20
Assume that $B\in R^{p\times6}$

Denote$$Y_i=BX_i\sim N_p(B\mu,B\Sigma B')$$

Then
$$\bar{Y}=\frac{1}{n}\sum Y_i=B\times\frac{1}{n}\sum X_i=B\bar{X}$$

$$B(19S)B'=\sum_{i=1}^n(BX_i-B\bar{X})(BX_i-B\bar{X})'=\sum_{i=1}^n(Y_i-\bar{Y})(Y_i-\bar{Y})' \sim W_6(B\Sigma B',19)$$

### (a)
$$B(19S)B'=\sum_{i=1}^n(Y_i-\bar{Y})(Y_i-\bar{Y})'\sim W_6(B\Sigma B',19)$$

### (b)
$$B(19S)B'=\sum_{i=1}^n(Y_i-\bar{Y})(Y_i-\bar{Y})'\sim W_6(B\Sigma B',19)$$

## 4.22
### (a)
According to the CLT,
$$\bar{X}\sim N_p(\mu, \frac{1}{n}\Sigma)$$

### (b)
According to the CLT,
$$n(\bar{X}-\mu)'S^{-1}(\bar{X}-\mu)\sim \chi_p^2$$

## 5.1
### (a)
$$T^2=\sqrt{n}(\bar{X}-\mu)'S^{-1}\sqrt{n}(\bar{X}-\mu)$$
```{r}
n=4
p=2
X <- matrix(c(2,8,6,8,12,9,9,10), nrow = n)
mu <- matrix(c(7,11), nrow=p)
T2=sqrt(n)*t(colMeans(X)-mu)%*%solve(cov(X))%*%(sqrt(n)*(colMeans(X)-mu))
T2
```

### (b)
$$\frac{2}{2}\times\frac{T^2}{3}\sim F_{2,2}$$

### (c)
From $\Pr(\frac{2}{2}\times\frac{T^2}{3}>q)=1-\alpha$

We can obtain q

```{r}
alpha=0.05
q=qf(1-alpha,p,n-p)
q
```
Because $\frac{2}{2}\times\frac{T^2}{3}<q$, we accept $H_0$

## 5.2
Before $X$ is changed, $T^2$ is
```{r}
n=3
p=2
X <- matrix(c(6,10,8,9,6,3), nrow = n)
mu <- matrix(c(9,5), nrow=p)
T2=sqrt(n)*t(colMeans(X)-mu)%*%solve(cov(X))%*%(sqrt(n)*(colMeans(X)-mu))
T2
```

After $X$ is changed, $T^2$ is
```{r}
C <-matrix(c(1,1,-1,1), nrow = 2)
X <- X%*%t(C)
mu <- C%*%mu
T2=sqrt(n)*t(colMeans(X)-mu)%*%solve(cov(X))%*%(sqrt(n)*(colMeans(X)-mu))
T2
```

## 5.5
$$H_0:\mu'=[0.55,0.60]\leftrightarrow H_1:\mu'\ne[0.55,0.60]$$
```{r}
n=42
p=2
x_bar<-matrix(c(0.564,0.603), nrow = p)
mu<-matrix(c(0.55,0.60), nrow = p)
S<-matrix(c(.0144,.0117,.0117,.0146), nrow = p)
T2=n*t(x_bar-mu)%*%solve(S)%*%(x_bar-mu)
T2/(n-1)*(n-p)/p
```
From $\Pr(\frac{40}{2}\times\frac{T^2}{41}>q)=1-\alpha$

We can obtain q
```{r}
alpha=0.05
q=qf(1-alpha,p,n-p)
q
```

Because $\frac{40}{2}\times\frac{T^2}{41}<q$, we accept $H_0$

The result is consistent with Figure 5.1 because it is equivalent that we accept $H_0$ and $\mu$ falls into the confidence ellipse.

## 5.7
Simultaneous confidence intervals:
```{r}
data=read.table("T5-1.DAT")
alpha=0.05
n = dim(data)[1]
p = dim(data)[2]
X=as.matrix(data)
s=cov(X)
x_bar=colMeans(X)
for (i in 1:3)
{
  print(c(x_bar[i]-sqrt(p*(n-1)/(n-p)*qf(1-alpha,p,n-p))*sqrt(s[i,i]/n),x_bar[i]+sqrt(p*(n-1)/(n-p)*qf(1-alpha,p,n-p))*sqrt(s[i,i]/n)))
}
```

Borferroni intervals:
```{r}
for (i in 1:3)
{
  print(c(x_bar[i]-qt(1-alpha/(2*p),n-1)*sqrt(s[i,i]/n),x_bar[i]+qt(1-alpha/(2*p),n-1)*sqrt(s[i,i]/n)))
}
```
The Borferroni intervals are more precise than simultaneous confidence intervals.

## 5.8
The value of a:
```{r}
n=42
p=2
x_bar<-matrix(c(0.564,0.603), nrow = p)
mu<-matrix(c(0.55,0.60), nrow = p)
S<-matrix(c(.0144,.0117,.0117,.0146), nrow = p)
a=solve(S)%*%(x_bar-mu)
a
```
```{r}
T2_value=n*(t(a)%*%(x_bar-mu))%*%(t(a)%*%(x_bar-mu))*solve(t(a)%*%S%*%a)
T2_value
```
It is equal to $T^2$ in Exercise 5.5.